\documentclass[margin,line]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Nathaniel Bottman \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.5in}p{4in}}
215 Simonyi Hall & {\it Email:} \texttt{nbottman@math.ias.edu} \\     
School of Mathematics   & \\         
Institute for Advanced Study & \\       
1 Einstein Dr, Princeton, NJ 08540 \\  
\end{tabular}

\section{\sc Professional appointments}

{\bf Member, Institute for Advanced Study}, Princeton, NJ, 2016--2019.
\begin{itemize}
\item[] This will be a research-only appointment.
\end{itemize}

{\bf Postdoctoral Research Fellow, Princeton University}, Princeton, NJ, 2016--2019.

{\bf Instructor, Northeastern University}, Boston, MA, 2015--2016. \begin{itemize}
\item[] Duties include teaching two calculus classes and one graduate-level geometry class, and conducting research.
\end{itemize}


\section{\sc Research Interests}
Symplectic geometry, Fukaya categories, \(J\)-holomorphic curves, polyfolds, mirror symmetry

\section{\sc Education}
{\bf Massachusetts Institute of Technology}, Cambridge, MA \\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D., Mathematics, September 2015
\begin{list2}
\vspace*{.05in}
\item Dissertation topic:  ``Pseudoholomorphic quilts with figure eight singularity'' 
%\item Dissertation Topic:  ``Hierarchical Models for Multiple Ratings
%  in Performance-Based\\ \hspace*{1.23in} Student Assessments.'' 
\item Advisor:  Katrin Wehrheim
\end{list2}
\end{list1}

{\bf University of Washington}, Seattle, WA\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] B.S., Mathematics, B.A., Slavic Languages and Literatures, June 2010
\end{list1}


\section{\sc Honors and Awards}
National Science Foundation Mathematical Sciences Postdoctoral Research Fellowship, 2016--2019

National Science Foundation Graduate Research Fellowship, 2010--2015

University of Washington Dean's Medal, 2010 (given to the top graduating senior in the natural sciences)

Goldwater Scholarship, 2008

Davidson Fellowship, 2007

%University of Washington Freshman Medal, 2006 (given to the UW freshman with the top academic record)

\section{\sc Publication in preparation}
{\bf 2-associahedra.}  Nathaniel Bottman, expected Spring 2017.

{\bf Moduli spaces of witch balls.}  Nathaniel Bottman, expected Spring 2017.

\medskip

\section{\sc Publications}
{\bf Gromov compactness for squiggly strip shrinking in pseudoholomorphic quilts.}  Nathaniel Bottman, Katrin Wehrheim.  Preprint available at \texttt{http://arxiv.org/abs/1503.03486}.

{\bf Pseudoholomorphic quilts with figure eight singularity.}  Nathaniel Bottman.  Preprint available at \texttt{http://arxiv.org/abs/1410.3834}.

{\bf Elliptic solutions of the defocusing NLS equation are stable.}  Nate Bottman, Bernard Deconinck, Michael Nivala.  J. Phys. A 44 (2011), no. 28, 24 pp.

{\bf KdV cnoidal waves are spectrally stable.}  Nathaniel Bottman, Bernard Deconinck.  Discrete Contin. Dyn. Syst. 25 (2009), no. 4, 1163--1180.

\section{\sc Invited talks}
Mirror Symmetry Seminar, Kansas State University, March 2017.

Members Seminar, Institute for Advanced Study, December 2016.

Deformation Theory Seminar, University of Pennsylvania, Spring 2016 

Quantum Fields and String Seminar, Perimeter Institute, Spring 2016

Jonathan Weitsman's Seminar, Northeastern University, December 2015

University of Massachusetts, Boston; Mathematics Colloquium, November 2015

Summer School on Moduli Problems in Symplectic Geometry, IHES, July 2015

Columbia Symplectic Geometry, Gauge Theory, and Categorification Seminar, April 2015

Rutgers Geometry, Symmetry, and Physics Seminar, March 2015

AMS Sectional Meeting, Michigan State University, March 2015

Northeastern University Analysis and Geometry Seminar, January 2015

Harvard Gauge Theory Seminar, October 2014

S.\ T.\ Yau's Seminar, Harvard University, October 2014

Workshop on Moduli Spaces of Pseudo-holomorphic Curves II, Simons Center, June 2014

Northern California Symplectic Geometry Seminar, Stanford University, March 2014

University of Texas Geometry Seminar, February 2014

\section{\sc Other talks}

Graduate Workshop on Symplectic and Contact Topology, Simons Center, October 2012

MIT and Princeton graduate student seminars, Fall 2011.

\section{\sc Teaching}

Instructor, Math 2321 (multivariable calculus for engineers), Northeastern University, Fall 2015.

Recitation instructor, 18.01A/02A (single- and multivariable calculus), MIT, Fall 2013.  Overall rating {\bf 6.5/7.0}.

Teaching assistant, Math 334/5/6 (second-year accelerated honors calculus), University of Washington, September 2008--June 2009.

\section{\sc Activities organized}
Co-organizing the Symplectic Geometry Seminar at the IAS and Princeton University during 2016--17.

Co-organized a Special Session on Moduli Spaces in Symplectic Geometry at the 2016 Joint Mathematical Meetings in Seattle, WA.

Co-organized the Geometry, Physics, and Representation Theory Seminar at Northeastern during 2015--16.

Co-organized a learning seminar with Katrin Wehrheim in Spring 2014 at UC Berkeley on symplectic convolution, in which 5 participants took turns lecturing.

Co-organized the 2013 MIT-RTG Geometry Workshop in Big Bear Lake, CA.  With five other MIT students, arranged a weeklong workshop where 30 graduate students and postdocs lectured on mirror symmetry, under the supervision of Mark Gross.

Organized the MIT Symplectic Coffee Seminar during Spring 2013.  Invited speakers and arranged the logistics for a weekly research seminar.

Co-organized the 2012 MIT-RTG Geometry Workshop in Watsonville, CA.  With Jiayong Li, arranged a weeklong workshop where 35 graduate students and postdocs lectured on the theory of polyfolds, under the supervision of Helmut Hofer.

\end{resume}
\end{document}




